Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-17 paper/v2.0/sections/1_introduction.tex
Correct eq15
Correction sec3 and sec4

Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}. However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity. At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
In these instances, a more accurate treatment needs to adopt. Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}. Here the applied high-intensity  electromagnetic field identify as the dressing field.

>>>>

Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}. However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity. At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
In these instances, a more accurate treatment needs to be adopted. Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}. Here the applied high-intensity  electromagnetic field identify as the \textit{dressing field}.

### 2021-08-17 paper/v2.0/sections/4_inverse_scattering_time.tex
Correction sec3 and sec4

Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix. Subsequently we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics. Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
\begin{equation} \label{eq:16}
 \Gamma^{00}_{N}(\varepsilon,k_x) =
 \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
which simplifies to
\begin{equation} \label{eq:17}
 \begin{aligned}
   &\Gamma^{00}_{N} (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \quad\times
   \int_{-\infty}^{\infty} d k_1 \Bigg[
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
   \\
   & \quad\times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
 \end{aligned}
\end{equation}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a  frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

\begin{figure}[b]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
\begin{equation} \label{eq:18}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
\end{equation}
Then we write the central element of inverse scattering time matrix in the more compact form
\begin{equation} \label{eq:19}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq:20}
    \Lambda_N(k_x) =
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
which can be evaluated with
\begin{widetext}
\begin{equation} \label{eq:21}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.

>>>>

Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix. Subsequently we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics. Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
\begin{equation} \label{eq:16}
 \Gamma^{00}_{N}(\varepsilon,k_x) =
 \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N,
\end{equation}
which simplifies to
\begin{widetext}
  \begin{equation} \label{eq:17}
   \begin{aligned}
     &\Gamma^{00}_{N} (\varepsilon,k_x) =
     \frac { \varrho^2}{eB}
     \delta(\varepsilon - \varepsilon_{N})
     \int_{-\infty}^{\infty}
     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
     \left|
     \int_{-\infty}^{\infty}
     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
     \chi_N \bm{\left(} \frac{\hbar}{eB}
     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
     dk_2 \right|^2 d k_1.
   \end{aligned}
  \end{equation}
In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
\begin{equation} \label{eq:18}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
\end{equation}
Then we write the central element of inverse scattering time matrix in the more compact form
\begin{equation} \label{eq:19}
  \begin{aligned}
    &\Gamma^{00}_{N}(\varepsilon,k_x) =
     \varrho
      \left[
      \int_{-\infty}^{\infty}
      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
      \left|
      \int_{-\infty}^{\infty}
      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
      dk_2 \right|^2
      dk_1
      \right]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq:20}
    \Lambda_N(k_x) =
    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
which can be evaluated with
\begin{equation} \label{eq:21}
    \Lambda_N (k_x) =
    \left[
    \frac
    {
      \int_{-\infty}^{\infty}
      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
      \left|
      \int_{-\infty}^{\infty}
      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
      dk_2 \right|^2
      dk_1
    }
    {
      \int_{-\infty}^{\infty}
      \left|
      \int_{-\infty}^{\infty}
      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
      dk_2 \right|^2
      dk_1
    }
    \right]^{1/2}.
\end{equation}
\end{widetext}

\begin{figure}[h!]
\includegraphics[scale=0.68]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\end{figure}
\begin{figure}[t!]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$. In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
\end{figure}

Normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
